---
title: "Introduction to StatComp20076"
author: "Jinwen Wu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20076}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp20076__ is a simple R package developed to carry out two functions (implemented through the R package _Rcpp_) for the 'Statistical Computing' course. Two functions are considered, namely, _GetAcf_ and _rec_char_.

The source R code for _GetAcf_ is as follows:
```{r,eval=FALSE}
GetAcf <- function(x, lag.max = 10){
  rm(list = ls())
  tmp <- sample(c(1:100), 50, replace = T)
  sampleT <- length(x)
  lag.max <- min(lag.max, sampleT - 1L)
  if(lag.max < 0){
    stop("lag.mx must be non-negative...")
  }
  lagList <- 0:lag.max
  muX <- mean(x)
  sigmaX <- sd(x)
  smpAcfCalc <- function(lagNum){
    smp1 <- x[1: (sampleT - lagNum)]
    smp2 <- x[(lagNum + 1) : sampleT]
    curNumerator <- sum((smp1 - muX) * (smp2 -muX)) / (sampleT - lagNum)
    curdivisor <- (sd(smp1)* sd(smp2))* (sampleT - lagNum -1) / (sampleT - lagNum)
    curAcf <- curNumerator / curdivisor
    return(curAcf)
  }
  res <- sapply(lagList, FUN = smpAcfCalc)
  return(res)
}
```

The function acf computes (and by default plots) estimates of the autocovariance or autocorrelation function. Function pacf is the function used for the partial autocorrelations. Function ccf computes the cross-correlation or cross-covariance of two univariate series.
"x" is a univariate or multivariate numeric time series object or a numeric vector or matrix
"lag.max" is the maximum lag at which to calculate the acf. Default is 10*log10(N/m) where N is the number of observations and m the number of series. Will be automatically limited to one less than the number of observations in the series.

Here is a simple example:
```{r,eval=FALSE}
result <- GetAcf(tmp, lag.max = 10)
result
```



The source R code for _rec_char_ is as follows:
```{r,eval=FALSE}
rec_char <- function(x){
  if (length(x)==1) return(x)
  return(c(tail(x,1),rec_char(x[-length(x)])))
}
```

This is a simple algorithm is used to turn the numbers.The parameter "x" is a vector of some positive integers

```{r,eval=FALSE}
char <- c('a','b','c','d')
rec_char(char)
```


